Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-02-24 Code/R/RMarkdown/Report_goodness-of-fit.Rmd
final corrections, added heatmap for p-values

library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(invgamma)
library(tidyverse)
library(scales)
library(RColorBrewer)
library(ggsci)
library(wesanderson)
library(ggpubr)
library(patchwork)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(geomtextpath)
library(latex2exp)
library(univariateML)
#install.packages('univariateML')
#univariateML::univariateML_models

@@

source("../MainFunctions/bootstrap_van_es_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator.r")
source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../MainFunctions/bootstrap_vasicek_estimator.r")
source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Programs/functions_sample_bias_mse.R")#

set.seed(1234567890, kind = "Mersenne-Twister")

@@

load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")

@@

fit.weibull <- fitdist(x1, "weibull")
plot(fit.weibull)
fit.weibull$aic
fit.norm <- fitdist(x1, "norm")
fit.norm$aic
plot(fit.norm)
```

```{r}
load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
x1<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x1)
mydata_dist
```

@@

```{r}
# load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
# x1<-as.vector(cv_values)
# n.sims <- 5
# 
# stats_gamma <- replicate(n.sims, {
#   r <- rgamma(n = length(x1),
#               shape = fit.gamma$estimate["shape"],
#               scale = fit.gamma$estimate["scale"]
#   )
#   estfit_gamma <- fitdist(r, "gamma") # Añadido para tener en cuenta los parámetros estimados
#   as.numeric(ks.test(r,
#                      "pgamma",
#                      shape = estfit_gamma$estimate["shape"],
#                      scale = estfit_gamma$estimate["scale"])$statistic
#   )
# })
# # Suponiendo que has ejecutado la simulación con la distribución gamma y guardado los resultados en stats_gamma
# 
# # Gráfico de la ECDF de las estadísticas de la prueba KS simuladas
# plot(ecdf(stats_gamma), las = 1, main = "KS-test statistic simulation (CDF) - Gamma Distribution", col = "darkorange", lwd = 1.7)
# grid()

<!-- ```{r} -->
<!-- # Suponiendo que ya has cargado los datos y ajustado la distribución Rayleigh -->
<!-- load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata") -->
<!-- x1 <- as.vector(cv_values) -->
<!-- n.sims <- 10 -->

<!-- stats_rayleigh <- replicate(n.sims, { -->
<!--   r <- rrayleigh(n = length(x1), -->
<!--                  scale = fit_rayleigh$estimate["scale"] -->
<!--   ) -->
<!--   estfit_rayleigh <- fitdist(r, "rayleigh") # Añadido para tener en cuenta los parámetros estimados -->
<!--   as.numeric(ks.test(r, -->
<!--                      "prayleigh", -->
<!--                      scale = estfit_rayleigh$estimate["scale"] -->
<!--                )$statistic -->
<!--   ) -->
<!-- }) -->

<!-- plot(ecdf(stats_rayleigh), las = 1, main = "KS-test statistic simulation (CDF) - Rayleigh Distribution", col = "darkorange", lwd = 1.7) -->
<!-- grid() -->

>>>>

library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(invgamma)
library(tidyverse)
library(scales)
library(RColorBrewer)
library(ggsci)
library(wesanderson)
library(ggpubr)
library(patchwork)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(geomtextpath)
library(latex2exp)
library(univariateML)
library(viridis)
#install.packages('univariateML')
#univariateML::univariateML_models

@@

source("../MainFunctions/bootstrap_van_es_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator.r")
source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../MainFunctions/bootstrap_vasicek_estimator.r")
source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Programs/functions_sample_bias_mse.R")# 
source("../imagematrix.R")
source("../imagematrix1.R")
set.seed(1234567890, kind = "Mersenne-Twister")

@@

load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")

@@

fit.weibull <- fitdist(x1, "weibull")
plot(fit.weibull)
fit.weibull$aic
# fit.norm <- fitdist(x1, "norm")
# fit.norm$aic
# plot(fit.norm)
```

```{r, eval=FALSE}
load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
x1<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x1)
mydata_dist
```

```{r cv5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland"}
load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
alpha <- 5.452
beta <- 2.061

pgamma_inv <- function(x, alpha, beta) {
  1 - pgamma(1/x, shape = alpha, rate = beta)
}

p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]

    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
  }
}

#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

#source("../imagematrix.R")
source("../imagematrix1.R")
#hist(p_values_matrix)
#par(mfrow=c(1,2))
#plot(imagematrix(p_values_matrix ))
plot(imagematrix1(p_values_matrix ))
#plot(imagematrix(p_values_matrix >0.1))
```

```{r Plot2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cv, window 7x7, Flevoland" }

load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")

ggplot() +
  geom_density(aes(x = as.vector(cv_values)), fill = "blue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
source("../imagematrix.R")
#hist(cv_values)
```

```{r, eval=FALSE}
load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")
x2<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```
```{r cv7, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 7x7, Flevoland"}
load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")
alpha <- 5.762
beta <- 2.611

pgamma_inv <- function(x, alpha, beta) {
  1 - pgamma(1/x, shape = alpha, rate = beta)
}

p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]

    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
  }
}

#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

source("../imagematrix.R")
#hist(p_values_matrix)
par(mfrow=c(1,2))
#plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
plot(imagematrix(p_values_matrix >0.1))
```

```{r, eval=FALSE}
load("../Programs/Data/results_data_Flevoland_cv_300_9.Rdata")
x2<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```

```{r cv9, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 9x9, Flevoland"}

#Los parametros fueron estimados con phitter.io
load("../Programs/Data/results_data_Flevoland_cv_300_9.Rdata")
alpha <- 3.58
beta <- 1.32

pgamma_inv <- function(x, alpha, beta) {
  1 - pgamma(1/x, shape = alpha, rate = beta)
}

p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]

    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
  }
}

#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

source("../imagematrix.R")
#hist(p_values_matrix)
par(mfrow=c(1,2))
#plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
plot(imagematrix(p_values_matrix >0.1))
```

```{r Plot3, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cv, window 5x5, Ottawa" }

load("../Programs/Data/results_data_Ottawa_cv_512_5.Rdata")

ggplot() +
  geom_density(aes(x = as.vector(cv_values)), fill = "red", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

```{r 5ottawa, eval=FALSE}
load("../Programs/Data/results_data_Ottawa_cv_512_5.Rdata")
x2<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```

```{r cvOttawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa"}

#Los parametros fueron estimados con phitter.io
load("../Programs/Data/results_data_Ottawa_cv_512_5.Rdata")
alpha <- 5.29
beta <- 2.20

pgamma_inv <- function(x, alpha, beta) {
  1 - pgamma(1/x, shape = alpha, rate = beta)
}

p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]

    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
  }
}

#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

source("../imagematrix.R")
#hist(p_values_matrix)
par(mfrow=c(1,2))
#plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
plot(imagematrix(p_values_matrix >0.1))
```

```{r Plotcqv, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cqv, window 5x5, Ottawa" }

load("../Programs/Data/results_data_Ottawa_cqv_512_5.Rdata")

ggplot() +
  geom_density(aes(x = as.vector(cv_values)), fill = "green", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

```{r 5ottawa_cqv, eval=FALSE}
load("../Programs/Data/results_data_Ottawa_cqv_512_5.Rdata")
x2<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```

```{r cqvOttawa_5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa"}

#Los parametros fueron estimados con phitter.io
load("../Programs/Data/results_data_Ottawa_cv_512_5.Rdata")
alpha <- 3.58
beta <- 1.32

pgamma_inv <- function(x, alpha, beta) {
  1 - pgamma(1/x, shape = alpha, rate = beta)
}

p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]

    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
  }
}

#save(x, p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

source("../imagematrix.R")
hist(p_values_matrix)
par(mfrow=c(1,2))
plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
plot(imagematrix(p_values_matrix >0.05))
```
```{r Plotcqvmad, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cqv, window 5x5, Ottawa" }

load("../Programs/Data/results_data_Ottawa_cd_mad_matrix_512_5.Rdata")

ggplot() +
  geom_density(aes(x = as.vector(cv_values)), fill = "pink", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

@@

### 2024-02-24 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
final corrections, added heatmap for p-values

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{mathtools}
   - \usepackage[utf8]{inputenc}
   - \usepackage{hyperref}
   - \hypersetup{draft}
   - \usepackage{float}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{mathabx}
   - \usepackage{subfig}
   #- \usepackage{caption}
   #- \captionsetup[table]{skip=0pt}
   - "\\setcitestyle{square,comma,numbers,sort&compress}" # citation style to numerical, work with \cite{} or [@]

@@

save(results_gi0, file = "./Data/resultsgi0.Rdata")

@@

load("./Data/resultsgi0.Rdata")

@@

Fig.&nbsp;\ref{fig:Real_SAR_Images}(a) shows the SAR image.
We used $7 \times 7$ local sliding windows for the test. In Fig.&nbsp;\ref{fig:Real_SAR_Images}(b), $p$-values higher than a $10\%$ significance level are shown. This approach allows to emphasize regions where there is not enough evidence against the null hypothesis. The new image reveals two distinct regions: darker background indicates homogeneity, while lighter backgrounds represent heterogeneous areas.
```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.',  fig.subcap=c('SAR image.', '$p$-values.' ), out.width='.48\\linewidth',  fig.ncol=2}
knitr::include_graphics("../../../Figures/PNG/Intensity.png")
knitr::include_graphics("../../../Figures/PNG/pvalue7x7-10.png")

>>>>

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{mathtools}
   - \usepackage[utf8]{inputenc}
   - \usepackage{hyperref}
   - \hypersetup{draft}
   - \usepackage{float}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{mathabx}
   - \usepackage{subfig}
   - \usepackage{subcaption}
   - \usepackage{caption}

   #- \captionsetup[table]{skip=0pt}
   - "\\setcitestyle{square,comma,numbers,sort&compress}" # citation style to numerical, work with \cite{} or [@]

@@

save(results_gi0, file = "./Data/resultsgi0_1.Rdata")

@@

load("./Data/resultsgi0_1.Rdata")

@@

Fig.&nbsp;\ref{fig:Real_SAR_Images}(a) shows the SAR image.
We used $7 \times 7$ local sliding windows for the test. 
In Fig. \ref{fig:Real_SAR_Images}(b), the heatmap of the $p$-values refers to the decisions at the $5\%$ significance level, with the orange areas representing a rejection of the null hypothesis, i.e., heterogeneous areas, while the blue areas representing non-rejection at the $5\%$ significance level, indicating homogeneity.
```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.',  fig.subcap=c('SAR image.', '$p$-values.' ), out.width = c("40mm", "60mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
knitr::include_graphics("../../../Figures/PNG/Intensity.png")#out.width='.55\\linewidth'
knitr::include_graphics("../../../Figures/PDF/color7x7.pdf")
